Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-13 paper.qmd
Updated Chen's paper citation
Initial writeup for the application intro

```{r}
#| label: hexbin-two-curvy
## Compute hexbin parameters
num_bins_x_two_curvy <- 27

@@

benchmark_two_curvy <- 2.5 * bin_width

@@

XXX WHY THESE EXAMPLES. NEEDS AN OVERVIEW PARAGRAPH

>>>>

```{r}
#| label: hexbin-two-curvy
## Compute hexbin parameters
num_bins_x_two_curvy <- 23

@@

benchmark_two_curvy <- 2.8 * bin_width

@@

<!-- XXX WHY THESE EXAMPLES. NEEDS AN OVERVIEW PARAGRAPH -->

To showcase the robustness of our method, this section presents two case studies. These applications were chosen to highlight various types of data where NLDR techniques play a critical role. The first case study explores single-cell data, a domain characterized by high-dimensional, sparse, and complex data structures. The second case focuses on the classic hand-written digits dataset, which provides an interpretable and visually intuitive benchmark for comparing NLDR techniques.
